\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-15 paper/figures.tex
Figures

\newcommand{\FigOverview}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Overview}\,---\, %
    }
    \label{fig:overview}
\end{figure*}
}

\newcommand{\FigHighLevel}{
\begin{figure}[t]
    \centering
    \vspace{-0.525in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{Overview}---%
      An ISP deploys a \scheme station, which sees a passive tap of network traffic.
      Clients request service by embedding a steganographic message in a TLS connection with any reachable site at the ISP\@. The client then connects
      to an unused IP address in the client's AS, and the station
      injects packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}

@@

\newcommand{\FigImplementation}{
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\, %
    }
    \label{fig:implementation}
\end{figure}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,%
      \TODO{Caption}
    }
    \label{fig:overview}
\end{figure}
}

\newcommand{\FigHighLevel}{
\begin{figure}[t]
    \centering
    \vspace{-0.54in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{\scheme Overview}---%
      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
      Following a steganographic registration process, a client can connect
      to an unused IP address in the ISP's AS, and the station will
      inject packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}

@@

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
      \TODO{Caption}
    }
    \label{fig:implementation}
\end{figure}
}
